% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%% Begin Table of Contents Page
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \renewcommand\contentsname{Table of Contents} % This command changes the name of the autogenerated table of contents (next line) from "Contents" to "Table of Contents".
% \tableofcontents % This command automatically generates the table of contents based on the sections in the document.
% \pagebreak[4]

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%% End Table of Contents Page
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%% Begin List of Figures Page
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \phantomsection % Create a phantom section such that the 'List of Figures' may be properly added to the table of contents.
% \addcontentsline{toc}{section}{List of Figures} % Add this section, 'List of Figures', to the table of contents.
% \listoffigures % This command automatically generates the list of figures based on the figures in the document.
% \pagebreak[4]

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%% End List of Figures Page
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%% Begin List of Tables Page
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \phantomsection % Create a phantom section such that the 'List of Tables' may be properly added to the table of contents.
% \addcontentsline{toc}{section}{List of Tables} % Add this section, 'List of Tables', to the table of contents.
% \listoftables % This command automatically generates the list of tables based on tables in the document.
% \pagebreak[4]

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%% End List of Tables Page
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\copyrightpage

\tableofcontents

\listoffigures

\listoftables

\begin{abstract}
\input{./tex/abstract}
\end{abstract}

\begin{dedication}
\vspace*{\fill}
\begin{center}
A loving dedication.
%I would like to dedicate this work, first and foremost, to my wife, Jennifer Black.
%She has supported me through all the good and bad
\end{center}
\vspace*{\fill}
\end{dedication}

\begin{acknowledgements}
I would like to acknowledge Vytas SunSpiral, whom was the catalyst for my endeavors into tensegrity robotics.
Without his constant hard work and support, both financially and mentally, I would not have been able to achieve this goal.
He has always had my best interests at heart, and he never stopped believing in me.

My UCSC advisors, Mircea Teodorescu and Gabriel Elkaim.
Without Dr. Elkaim, I would have never gotten connected with Vytas SunSpiral, and Dr. Teodorescu has supported me through the final stages of my degree. 

I would also like to acknowledge all the people whom I have collaborated with.
Ken Caluwaerts, Jeffrey Fresien, Atil Iscen, Andrew Sabelhaus, Adrian Agogino, Steve Lessard, Marvin Zhang, Xinyang (Young) Geng, Paul Glick, Michael Fanton, and Massimo Vespignani.
Whom have given me inspiration, fueled discussion, and support over the years.

The text of this thesis includes reprints of the following previously published
material: \cite{NIACfinalreport, Vytas_IPPW_2013, bruce2014design, iscen2015learning, sabelhaus2015system, caluwaerts2016esitmation, geng2016deep}

\end{acknowledgements}